Compare pseqs

### 2019-05-29 comparepseqs.Rmd
Allow set included variables for import

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs",
            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

@@

    if (!file.exists(paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))) {
        missing$alphadistribution = TRUE
    } else {
        alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))
    }

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]])
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

@@

>>>>

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs")#,
#            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

@@

    if (!file.exists(paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))) {
        missing$alphadistribution = TRUE
    } else {
        alphadistribution <- readRDS(file =
                                         paste0("rds-comparepseqs/alphadistribution-",
                                                key , ".rds"))
    }

    ret[[key]] = list(                      "alphadistribution" = alphadistribution)
    }

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]],
                                   included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                                "CURR_SMOKE", "BL_USE_RX_C09",
                                                "Q57X", "BL_USE_RX_C03",
                                                "BL_USE_RX_C07", "BL_USE_RX_C08"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

@@

scatterplot.df %>% head

 lapply(ret, function(x) x$alphadistribution %>% head)
